### 2013-03-18 doc/final_report/design.tex
Finished first draft of testing chapter and rearranged contents

\subsection{ Process Model }

\subsection{ System Design }

\subsection{}

>>>>

\section{ System Architecture}

It was decided from the outset that Partridge would be a web-based tool.
Web-based systems can generally be run on any computer with access to the
internet and a modern web browser. This also means that there is no need for
the end user to install or configure extra software on their computers, making
Partridge accessible to non-technical users and those who have aggressive
software restrictions on their computers, such as GPs and users of public
computers in libraries or on academic sites.

\section{ Subsystem Design }

\subsection{ Preprocessor }

\subsection{ Web Backend }

\subsection{ Web Frontend }

### 2013-03-18 doc/final_report/implementation.tex
Finished first draft of testing chapter and rearranged contents

\subsection{Technical Challenges}

\subsubsection{ Sourcing Scientific Papers}
For Partridge to be a success, it is important to include a large variety of
different scientific papers in its corpus. Therefore, several sources of
scientific papers were explored and considered.

@@

\subsubsection{Acquiring Scientific Papers}
Once PLOSOne was identified as a suitable source of papers, a method for
acquiring large batches of papers to be processed was formulated.

\subsubsection{PDF Conversion}
Most scientific papers available on the internet are formatted as PDF
documents. However, Partridge uses and stores documents that use the CoreSC
schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
spike work was carried out to determine the feasibility of converting papers
published as PDF documents into XML documents. Townsendi \emph{et al.} (2009) liken converting
PDF to XML to ``converting hamburgers into cows," they go on to explain that
PDF documents do not contain any semantic data and documents lose much of their
explicit structure when they are formatted in this way \cite{Townsend2009}.
Therefore, to convert PDF documents into an NLP-friendly format, some
heuristics must be used to detect the document's structure\cite{pdfminer}.

@@

\subsubsection{Pre-processing with SAPIENTA}

@@

>>>>

\section{Paper Preprocessor}

\subsection{ Sourcing and Acquiring Scientific Papers}
For Partridge to be a success, it is important to include a large variety of
different scientific papers in its corpus. Therefore, several sources of
scientific papers were explored and considered.

@@

\subsection{Format Conversion}
Most scientific papers available on the internet are formatted as PDF
documents. However, Partridge uses and stores documents that use the CoreSC
schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
spike work was carried out to determine the feasibility of converting papers
published as PDF documents into XML documents. Townsendi \emph{et al.} (2009) liken converting
PDF to XML to ``converting hamburgers into cows," they go on to explain that
PDF documents do not contain any semantic data and documents lose much of their
explicit structure when they are formatted in this way \cite{Townsend2009}.
Therefore, to convert PDF documents into an NLP-friendly format, some
heuristics must be used to detect the document's structure\cite{pdfminer}.

@@

\subsection{Pre-processing with SAPIENTA}

@@

\subsection{Paper Type Classification}

\subsection{ Paper Processing Notifications }

\section{ Web Backend }

\subsection{ Server Views }

\subsection{Database Interaction \& SQLAlchemy}

\subsection{Data version control \& Alembic}

\subsection{WSGI and Apache Integration}

\section{Web Frontend}

\subsection{Query Interface}

\subsection{ Paper Upload Interface }

\subsection{ Bookmarklet }

### 2013-03-18 doc/final_report/introduction.tex
Finished first draft of testing chapter and rearranged contents

Partridge's main objective is to provide reading recommendations and
information retrieval for scientists and researchers. This should reduce the
amount of extraneous information that users have to read for themselves by
helping them find information specific to their interests more quickly.
Partridge will achieve this through the use of several existing techniques in
Natural Language Processing which are discussed below.

As well as helping users locate files, Partridge will also

@@

>>>>

@@

Partridge's main objective is to provide reading recommendations and
information retrieval for scientists and researchers. This should reduce the
amount of extraneous information that users have to read for themselves by
helping them find information specific to their interests more quickly.
Partridge will achieve this through the use of several existing techniques in
Natural Language Processing and utilisation of SAPIENTA as discussed above.

### 2013-03-18 doc/final_report/methodology.tex
Finished first draft of testing chapter and rearranged contents

\subsection{Development Methodology}

\subsubsection{Existing Methodologies}
Selecting a suitable development methodology for building Partridge is another
very important choice for the project.

@@

\subsubsection{ Partridge's Development Methodology}

@@

\subsubsection{ Work Timeline }

>>>>

\section{Existing Methodologies}
Selecting a suitable development methodology for building Partridge is another
very important choice for the project.

@@

\section{ Partridge's Development Methodology}

@@

\subsection{ Work Timeline }

### 2013-03-18 doc/final_report/testing.tex
Finished first draft of testing chapter and rearranged contents

\subsection{ Backend \& Infrastructure Testing}

@@

In cases where Partridge calls remote services, reuses code that has already
been tested, or calls code that runs heavy computation, it can be inconvenient
or unhelpful to run unit tests that trigger these behaviours. To save time,
\emph{Mock}\cite{mock2013} was used for verifying these behaviours were being
called correctly instead.  \emph{Mock} allows the arbitrary replacement of Python
routines and objects with `mock' objects that mimic the behaviour of the
original routine and store information on how they were called or used. This
meant that calls to long-running routines and functions that already have tests
can be validated and a fake return value sent back to the caller, without
having to actually execute the code. This technique was used heavily in the
paper processor which calls SAPIENTA and PDFX and also wraps several data
classes which have their own unit tests.

\subsection{ Selenium \& Frontend Testing }

The frontend parts of Partridge that were written in Javascript and HTML5 also
had to be tested to verify that the query and upload forms behaved as expected.

@@

Once a basic user interface had been implemented, the system was opened for
user testing. The main Patridge instance
(\url{http://farnsworth.papro.org.uk/}) was advertised using several social
media streams and users encouraged to submit bug reports if they experienced
any problems whilst using the site.

@@

\subsection{ Result Presentation }

@@

\subsubsection{ Classifier Accuracy }

@@

\subsubsection{ Receiver Operating Characteristics Chart}

@@

\subsubsection{ Area Under Curve }

@@

\subsubsection{ Confusion Matrices}

@@

\subsubsection{ Precision, Recall and F-Measure }

>>>>

\subsection{ Back-end \& Infrastructure Testing}

@@

In cases where Partridge calls remote services, reuses code that has already
been tested, or calls code that runs heavy computation, it can be inconvenient
or unhelpful to run unit tests that trigger these behaviours. To save time,
\emph{Mock}\cite{mock2013} was used for verifying these behaviours were being
called correctly instead.  \emph{Mock} allows the arbitrary replacement of
Python routines and objects with `mock' objects that mimic the behaviour of the
original routine and store information on how they were called or used. This
meant that calls to long-running routines and functions that already have tests
can be validated and a fake return value sent back to the caller, without
having to actually execute the code. This technique also allows the isolation
of problems within the caller code and its commmunication with the target
functions and will pass even if the target code is broken provided that the
caller code is correct\cite{saff2004mock}. The Mock testing technique was used
heavily in the paper processor which calls SAPIENTA and PDFX and also wraps
several data classes which have their own unit tests.

Partridge's web views were tested using \emph{Flask}'s in-built test client.
This is an object attached to the \emph{Flask} app that can be used to emulate
a call to a particular view\cite{flask2012}. Cookies and form information can also be
manipulated through this client, enabling comprehensive testing of each of the backends
for Partridge's query, paper upload and bookmarklet capabilities.

\subsection{ Selenium \& Front-end Testing }

The frontend parts of Partridge that were written in Javascript and HTML5 also
had to be tested to verify that the query and upload forms behaved as expected.
Selenium\cite{seleniumide} was selected to facilitate these tests.

Selenium is a browser-based unit testing framework that allows developers to
script actions that a user might undertake whilst browsing a website. Tests for
selenium can be written in Firefox using the Selenium IDE framework. These
tests can then be exported as HTML files with embedded javascript instructions
and executed in any other browser to test compatibility with the product under
test.

During the development of Partridge, several suites of tests were written using
Selenium to verify that the query form, paper upload form and bookmarklet code
behave as expected. Not only do these tests verify the behaviour of the HTML
and javascript interface, but they also helped to check the higher level
functionality of Partridge. For example, the test suite for the Partridge query
form also helps to verify that query backend is working correctly. The Selenium
tests were executed as part of the integration process when a new feature was
added to Partridge.

@@

Raymond(1999) suggests that as the developer of an open source project,
``Treating your users as co-developers is your least-hassle route to rapid code
improvement and effective debugging\cite{raymond1999cathedral}." Partridge
hasn't been developed using an open methodology since, as a dissertation
project, it has been necessary to avoid complications around work ownership.
However, Raymond's notion that software should be released early and often and
tested on its user-base is an effective one and has been widely adopted by both
open and closed source developers\cite{linux2013}\cite{unity2013}.

As soon as Iteration 1 was complete, Partridge was made open for user testing
and the primary Patridge instance (\url{http://farnsworth.papro.org.uk/}) was
advertised using several social media streams. It was made clear to any early
adopting users that the system was still in development and they were
encouraged to submit bug reports if they experienced any problems whilst using
the site. This was a great success and a number of bugs and suggested
improvements were raised both via the GitHub repository\cite{softlybug2013} and
in conversation, helping to improve Partridge and find some defects that had
previously been overlooked.

@@

\subsection{ Evaluation Result Analysis }

@@

\subsection{ Classifier Accuracy }

@@

\subsection{ Receiver Operating Characteristics Chart}

@@

\subsection{ Area Under Curve }

@@

\subsection{ Confusion Matrices}

@@

\subsection{ Precision, Recall and F-Measure }
